---
format:
  pdf:
    papersize: <PAPER_SIZE>
    geometry: margin=1in
    fontsize: <FONT_SIZE>
    mainfont: "Lato"  # choose your font
    linestretch: 1.15
    colorlinks: true
    urlcolor: black
execute:
  echo: false
  warning: false
  message: false
---

```{r setup}
#| include: false
library(tidyverse)
library(knitr)
library(kableExtra)
library(readr)

# Function to format publications with proper spacing and consistent font
format_publications <- function(data) {
  # Create citations
  citations <- data %>%
    arrange(desc(year)) %>%
    mutate(
      citation = paste0(
        authors, " (", year, "). ",
        title, ". ",
        journal
      )
    ) %>%
    pull(citation)
  
  # Create a data frame with blank rows between citations
  n_citations <- length(citations)
  formatted_df <- data.frame(
    citation = character(n_citations * 2 - 1)
  )
  
  # Fill in citations and blank rows
  for(i in 1:n_citations) {
    formatted_df$citation[2*i - 1] <- citations[i]
    if(i < n_citations) {
      formatted_df$citation[2*i] <- ""  # Insert blank row
    }
  }
  
  # Create table with kable
  formatted_df %>%
    kable(format = "pipe", 
          col.names = NULL) %>%
    kable_styling(font_size = 11,
                  full_width = TRUE,
                  bootstrap_options = "condensed") %>%
    column_spec(1, width = "6.5in")
}

# Function to create tables with consistent styling
create_table <- function(data, widths = NULL, align = NULL) {
  if (is.null(align)) {
    align = rep("l", ncol(data))
  }
  
  total_width <- sum(as.numeric(gsub("in", "", widths)))
  if (total_width > 6.5) {
    scaling_factor <- 6.5 / total_width
    widths <- paste0(as.numeric(gsub("in", "", widths)) * scaling_factor, "in")
  }
  
  tbl <- data %>%
    kable(format = "pipe", 
          align = align,
          col.names = NULL,
          escape = FALSE) %>%
    kable_styling(font_size = 11,
                  full_width = TRUE,
                  bootstrap_options = "condensed")
  
  if (!is.null(widths)) {
    for (i in 1:length(widths)) {
      tbl <- tbl %>% column_spec(i, width = widths[i])
    }
  }
  
  return(tbl)
}
```

::: {style="text-align: center; margin-bottom: 20pt"}
# John Doe

Assistant Professor\
Department of Blah_blah\
National University of Blah_blah\
johndoe\@blah.edu • [your_website_url_if_you_have]

*Last Updated: December <YEAR>*

:::

# EDUCATION

```{r}
tribble(
  ~Degree, ~Year, ~Institution, ~Location,
  "Ph.D. in ??", "<YEAR>", "University of ABC", "USA",
  "Master of ??", "2016", "National University of ABC", "Singapore",
) %>%
  arrange(desc(Year)) %>%
  create_table(widths = c("2.5in", "0.7in", "2.5in", "0.8in"))
```

# RESEARCH INTERESTS

-   Blah blah
-   Blah blah

# ACADEMIC APPOINTMENTS

```{r}
tribble(
  ~Years, ~Position, ~Institution,
  "<YEAR>-present", "Assistant Professor, Department of ABC", "National University of ABC",
  "2023-2024", "Research Fellow", "<org>",
) %>%
  create_table(widths = c("1.2in", "2.8in", "2.5in"))
```

# PUBLICATIONS

## Peer-Reviewed Journal Articles 

```{r}
read_csv("pub_published_table.csv") %>%
  format_publications()
```


# RESEARCH FUNDING AND AWARDS

```{r}
tribble(
  ~Year, ~Award, ~Institution, ~Amount,
  "<YEAR>", "Blah blah", "<org>", "$15000",
  "<YEAR>", "Blah blah", "<org>", "",
) %>%
  arrange(desc(Year)) %>%
  create_table(widths = c("0.8in", "2.3in", "2.5in", "0.9in"))
```

# RESEARCH PROJECTS

```{r}
read_csv("research_proj.csv") %>%
  arrange(desc(year)) %>%
  select(`funder/collaborator`, project, year, role) %>%
  create_table(widths = c("1.3in", "3in", "0.8in", "1.4in"))
```

# TEACHING EXPERIENCE

## Primary Instructor

```{r}
tribble(
  ~Year, ~Course, ~Institution,
  "<YEAR>", "SW3224 <name of course>", "NUS",
  "<YEAR>", "SW4103 <name of course>", "NUS",
) %>%
  create_table(widths = c("1in", "3in", "2.5in"))
```



# SERVICE AND PROFESSIONAL ACTIVITIES

## Research Consultancy

```{r}
tribble(
  ~Year, ~Organization, ~Role,
  "<YEAR>-<YEAR>", "ABC org", "Research Consultant",
  "2017-2018", "<org>", "Research Consultant",
) %>%
  create_table(widths = c("1.2in", "3in", "2.3in"))
```


